
% Don't like 10pt? Try 11pt or 12pt
\documentclass[10pt]{article}
\usepackage{calc}
\usepackage{comment}

% Simpler bibsection for CV sections
% (thanks to natbib for inspiration)
\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em} %1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}%
        {\begin{enumerate}{}{%
%        {\begin{list}{}{%
       \setlength{\leftmargin}{\bibhang}%
       \setlength{\itemindent}{-\leftmargin}%
       \setlength{\itemsep}{\bibsep}%
       \setlength{\parsep}{\z@}%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{enumerate}\vspace{-.6\baselineskip}}
%        {\end{list}\vspace{-.6\baselineskip}}
\makeatother

% Layout: Puts the section titles on left side of page
\reversemarginpar



%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

\usepackage[shortlabels]{enumitem}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

\newcommand{\makeheading}[2][]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
             {\large \bfseries #2 \hfill #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

% The section headings
%
% Usage: \section{section name}
\renewcommand{\section}[1]{\pagebreak[3]%
    \hyphenpenalty=10000%
    \vspace{1.3\baselineskip}%
    \phantomsection\addcontentsline{toc}{section}{#1}%
    \noindent\llap{\scshape\smash{\parbox[t]{\marginparwidth}{\raggedright #1}}}%
    \vspace{-\baselineskip}\par}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1,leftmargin=*]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt]}
        {\end{itemize}}

% An environment IDENTICAL to innerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{loneinnerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt]}
        {\end{itemize}\vspace{-.6\baselineskip}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[3]}
\newcommand{\halfblankline}{\quad\vspace{-0.5\baselineskip}\pagebreak[3]}

% Uses hyperref to link DOI
\newcommand\doilink[1]{\href{http://dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi:\doilink{#1}}

% For \url{SOME_URL}, links SOME_URL to the url SOME_URL
\providecommand*\url[1]{\href{#1}{#1}}
% Same as above, but pretty-prints SOME_URL in teletype fixed-width font
\renewcommand*\url[1]{\href{#1}{\texttt{#1}}}

% For \email{ADDRESS}, links ADDRESS to the url mailto:ADDRESS
\providecommand*\email[1]{\href{mailto:#1}{#1}}
% Same as above, but pretty-prints ADDRESS in teletype fixed-width font
%\renewcommand*\email[1]{\href{mailto:#1}{\texttt{#1}}}

%\providecommand\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
%    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
%\providecommand\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
%    \TeX}}
\providecommand\BibTeX{{B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    \TeX}}
\providecommand\Matlab{\textsc{Matlab}}

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makeheading{Issam H. Laradji \hfill Curriculum vitae}

\section{Contact Information}

% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table
%       (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{1.4in}%
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
%\href{http://www.cse.osu.edu/}%
%     {Department of Computer Science and Engineering} & \\
%\href{http://www.osu.edu/}{The Ohio State University}
Vancouver, BC,  Canada  & (778) 232-0212 \\ \email{issam.laradji@gmail.com}\\
\end{tabular}

%\section{Objective}

%Insert text here if you want to
%\begin{innerlist}
%\item More information and auxiliary documents can be found at\\\url{http://www.tedpavlic.com/facjobsearch/}
%\end{innerlist}

\section{Profile}
I am currently a PhD research student in the UBC Machine Learning lab of my supervisor Mark Schmidt.\\

My research work involves large-scale machine learning, optimization, deep learning, and applying current and new data science methods to real-life datasets.



\section{Education}


{\bf Ph.D.} in Computer Science (UBC),  \hfill Sep 2014 - Aug 2019 (Expected)
             
        \begin{innerlist}
        \item University of British Columbia
        \item Supervisor: {Mark Schmidt}
        \item \emph{GPA: 4.0/4.0}
        \item Average Grade: 95.6 \%\\
        \end{innerlist}
 {\bf M.Sc.} in Information \& Computer Science, \hfill {Sep 2012 to May 2014}
        
       \begin{innerlist}
        \item King Fahd University of Petroleum \& Minerals
        \item Thesis Topic: \emph{New Algorithms for Deep Learning Machines}
        \item Advisor:
              \href{http://faculty.kfupm.edu.sa/ICS/lahouari/Default.htm}
                   {Dr. Lahouari Ghouti}
        \item \emph{GPA: 4.0/4.0}\\
        \end{innerlist}

 {\bf B.Sc.} in Information \& Computer Science, \hfill {Feb 2008 to Aug 2012}
        \begin{innerlist}
        \item King Fahd University of Petroleum \& Minerals
        \item \emph{GPA: 3.647/4.0}
        \item \emph{Last two years GPA:  4.0/4.0}
        \end{innerlist}


\section{Publications}
\vspace{-.1275in}
\begin{bibsection}
    \item {\bf Coordinate Descent Converges Faster with the Gauss-Southwell Rule Than Random Selection.}
    Nutini, Julie, Mark W. Schmidt, {\bf Issam H. Laradji}, Michael P. Friedlander, and Hoyt A. Koepke.  {\it ICML}, 2015.

    \item {\bf Convergence Rates for Greedy Kaczmarz Algorithms, and Randomized Kaczmarz Rules Using the Orthogonality Graph.} Nutini, Julie, Behrooz Sepehry, {\bf Issam H. Laradji}, Mark W. Schmidt, Hoyt A. Koepke and Alim Virani. {\it UAI }, 2016.



    \item {\bf Software defect prediction using ensemble learning on selected features.} {\bf Laradji, Issam H.}, Mohammad Alshayeb, and Lahouari Ghouti. {\it Elsevier IST},  2015.

    \item {\bf Perceptual hashing of color images using hypercomplex representations.} {\bf Laradji, Issam H.}, Lahouari Ghouti, and El-Hebri Khiari. {\it IEEE ICIP}, 2013.
        
    \item {\bf Sparse Single-Hidden Layer Feedforward Network for Mapping Natural Language Questions to SQL Queries.} {\bf Laradji, Issam H.}, Lahouari Ghouti, Faisal Saleh, and Musab A. AlTurki. {\it Springer ICANN }, 2014.

    \item {\bf XML classification using ensemble learning on extracted features.} {\bf Laradji, Issam H.}, Mohammed Salahadin, and Lahouari Ghouti. {\it ACM Southeast Regional Conference}, 2014.
    
\end{bibsection}


\vspace{0.2in}
% Add a little space to nudge next ``Conference Publications'' marginpar
% down to make room for tall ``Submitted Journal Publications''
% marginpar. If there are enough submitted journal publications, this
% space will not be needed (and should be removed).
%\vspace{0.1in}

\section{Selected Projects}

Mitacs-Accelerate Graduate Research Internship Program \hfill Jan 2016 - Oct 2016
\begin{innerlist}
    \item Optical Recognition of Anglers.\\
\end{innerlist}

Google Summer of Code 2014    
\begin{innerlist}
    \item Implemented and wrote the documentation for Neural Network algorithms for the sklearn python open-source library \footnote{Found here: http://scikit-learn.org/stable/modules/neural\_networks\_supervised.html}.\\
\end{innerlist}

 Independent Research Course
\begin{innerlist}
    \item Autonomous Helicopter Control using reinforcement learning methods.\\
\end{innerlist}

Kaggle data science competitions
\begin{innerlist}
    \item Implemented many data science algorithms for competitions on gender prediction from handwriting, natural language processing,  stock price prediction, and predicting cause-effect pairs.\\
\end{innerlist}



UBC Learning Analytics Hackathon 2.0 \hfill Jan 28-29, 2017
\begin{innerlist}
    \item Implemented a prototype for predicting what students are most interested in from a given course using tweets, students' viewing history, clicks, and discussions in the past offerings of the course.  \\
\end{innerlist}

SportsHack 2015 \hfill Nov 27-29, 2016
\begin{innerlist}
    \item Implemented a prototype for predicting the outcome of a play for CFL football players.
\end{innerlist}



\section{Selected Code in my Github Account}

\begin{innerlist}
\item Graphical Models\footnote{Found here: https://github.com/IssamLaradji}
\item Reinforcement Learning
\item Software Defect Prediction
\item Neural Networks
\item XML Classification 
\item PrettyPlots\\
\end{innerlist}



\section{Research Groups}

UBC Machine Learning Reading Group \footnote{Found here: http://www.cs.ubc.ca/labs/lci/mlrg/}
\begin{innerlist}
\item Organizing the group, maintaining its website, and regularly attending its weekly meetings.
\item Prepared and presented topics on graphical models, non-convex optimization, parallel algorithms, large-scale kernel methods, convolutional neural networks, kalman filters, and inverse reinforcement learning.\\
\end{innerlist}

UBC Machine Learning Theory Reading Group \footnote{Found here: https://www.cs.ubc.ca/labs/beta/Courses/MLTRG.html}
 \begin{innerlist}
\item Regularly attending its weekly meetings.
\item Prepared and presented topics on Radamcher Complexity, Support Vector Machine Theory, and Neural Networks Theory.
\end{innerlist}   

\section{Teaching Experience}

Workshop for a Tekathon ran by Illuminate Vancouver \hfill May 2017
\begin{innerlist}
    \item Ran a workshop on Python in Data Science, recommender systems, and intelligent chat bots.\footnote{https://github.com/IssamLaradji/Tekathon\_Workshop\_2017}\\
\end{innerlist}

Workshops for the ECE UBC Department \hfill Apr 2017
\begin{innerlist}
    \item Ran a workshop on Python and its applications in Data Science.
    \item Ran a workshop on Machine Learning Algorithms and Applications.\\
\end{innerlist}

UBC CS TA training event \hfill Sep 2016
\begin{innerlist}
    \item Facilitated the {\bf Time Management} session in the event.\\
\end{innerlist}

Instructional Skills Workshop \hfill Apr 2015
\begin{innerlist}
    \item Completed a 3-day intensive workshop that develops participant's teaching skills and confidence.\\
\end{innerlist}


CPSC 340 - Machine Learning and Data Mining
\begin{innerlist}
    \item Taught it 3 times: (Sep 2015 - Dec 2015), (Sep 2016 - Dec 2016), and (Jan 2016 - Current).
    \item Required to write Python code for the assignments, prepare and teach weekly tutorials, regularly engage with students in the discussion forums, and hold office hours, mark assignments and exams.\\
\end{innerlist}

CPSC 210 Software Construction \hfill Jul 2015 - Aug 2015
\begin{innerlist}
    \item Required to teach lab sections weekly where students were required to solve problems using JAVA.\\
\end{innerlist}

CPSC 221 Basic Algorithms and Data Structures  \hfill May 2015 - Jun 2015
\begin{innerlist}
   \item Required to teach lab sections weekly where students were required to solve problems using C++.\\
\end{innerlist}

CPSC 422 Advanced Artificial Intelligence \hfill Jan 2015 - Apr 2015
\begin{innerlist}
    \item Regularly engage with students in the discussion forums, hold office hours, mark assignments and exams.\\
\end{innerlist}

CPSC 322 Artificial Intelligence \hfill Sep 2014 - Dec 2014
\begin{innerlist}
    \item Regularly engage with students in the discussion forums, hold office hours, mark assignments and exams.

\end{innerlist}


\section{Achievements}

\textbf{Summer School 2017 in Deep Learning and Reinforcement Learning.}
\vspace{0.2in}

\textbf{Big Data University Innovation Prize won at SportsHack 2015.}
\vspace{0.2in}

\textbf{Master Kaggle Participant (Data Science Competition hub)} \hfill   {2014}
\begin{innerlist}
\item ``Master" Kaggler \footnote{http://www.kaggle.com/users/65920/issam-laradji}; ranked in the top 100 among more than 12,800 members in the year 2014. Notable performance in problems of Gender prediction from handwriting, Natural language processing,  Stock price prediction, and predicting Cause-effect pairs.


\end{innerlist}
\vspace{0.2in}
\textbf{AI Sandbox Capture the flag competition} \footnote{http://aisandbox.com/start/} \hfill   { Feb 2013}
\begin{innerlist}
\item Participated in an AI competition  to control a realistic team of bots. Ranked in the top 11 among more than seventy participants.

\end{innerlist}
\vspace{0.2in}
\textbf{Summer Project} 
\begin{innerlist}
\item Received Google Summer of Code 2014 grant for implementing Neural Network modules for a python open-source library \footnote{http://www.google-melange.com/gsoc/proposal/public/google/gsoc2014/issamou/5668600916475904}
\end{innerlist}
\vspace{0.2in}
\textbf{Online courses with statement of Accomplishment } 
\begin{innerlist}
\item {\bf Coursera}: ``Algorithms: Design and Analysis, Part 1", ``Machine Learning", \\``Introduction to Data Science", ``Coding the Matrix".
\item {\bf edX }:  ``Learning from Data".

  \end{innerlist}
  \vspace{0.2in}
\textbf{Undergraduate project: Agent-based Surveillance System} 
\begin{innerlist}
\item Developed a Java program that registers faces and can recognize them efficiently under different lighting. Earned first place in ``15th Saudi Technical Exchange Meeting" project competition.\\
  \end{innerlist}
{\bf Passed promotion exams of English and Math courses and was promoted to undergraduate level skipping preparatory year}\hfill   { Feb 2008 }\\\\


\section{Awards and Scholarships}
\begin{innerlist}
\item Graduate TA Award 2015 at the UBC Computer Science department.

\vspace{0.1in}
\item Google Summer of Code 2014 grant.

\vspace{0.1in}
\item UBC Four Year Fellowship (Awarded Jan 2015).

\vspace{0.1in}
\item Scholarship for M.Sc. studies at King Fahd University of Petroleum \& Minerals. 

\vspace{0.1in}
\item Scholarship for B.Sc. studies at King Fahd University of Petroleum \& Minerals. 
\end{innerlist}


\end{document}
